Combining information from photometric and spectroscopic data:\\ Probabilistic spectrophotometric inference

### 2015-06-04 tex/figures.tex
remove much of the introductory text, plotting for fully burned-in mocks
save summary figure to figs directory and add to ms

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/speconly_uncalibrated.pdf}
\caption{Results of inference from an \emph{uncalibrated} mock
  spectrum and a single photometric data point.  Panels and colors are
  as in Figure \ref{fig:speconly_calibrated}.  In this case the
  observed spectrum is in arbitrary units and the true
  calibration vector is not a constant with wavelength.
 {\color{red} This is not converged.}
\label{fig:speconly_uncalibrated}}
\end{figure*}

@@

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/vary_params.pdf}
\caption{Offset from the input parameters of the medians of the
posterior PDFs for model parameters obtained from mock spectra and
photometry. Lines connect a single model.
 \label{fig:mock_parameter_space}}
\end{figure*}

>>>>

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/speconly_uncalibrated.pdf}
\caption{Results of inference from an \emph{uncalibrated} mock
  spectrum and a single photometric data point.  Panels and colors are
  as in Figure \ref{fig:speconly_calibrated}.  In this case the
  observed spectrum is in arbitrary units and the true
  calibration vector is not a constant with wavelength.
\label{fig:speconly_uncalibrated}}
\end{figure*}

@@

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/vary_params.pdf}
\caption{Offset from the input parameters of the medians of the
posterior PDFs for  inference from mock spectra and
photometry, as a function of the mock parameter that is varied.
 \label{fig:mock_parameter_space}}
\end{figure*}
